Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-02-20 awipev-CO2.Rmd
new pH spectro from sf and dur updated in the dicrete_sample file + update of the sf calibration part

sfPeriod <-  sfPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600 *24)))%>%
  dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])

@@

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
                                ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
                                 ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
                                 ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
                                ifelse(datetime >= sfinterv[21] , 21,NA ))))))))))))))))))))))

@@

# # 5th period, pH spectro from 2018-04-16 07:00:00 must fit one  voltINT to calculate E0
# we put the mean of 4 previous days because voltINT was not present.
mean_voltINT_4d <- d_all%>%
  dplyr::filter(datetime >= "2018-04-11" & datetime <= "2018-04-14")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4d <- as.numeric(mean_voltINT_4d)
d_all$voltINT <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , mean_voltINT_4d, d_all$voltINT)

mean_voltEXT_4d <- d_all%>%
  dplyr::filter(datetime >= "2018-04-11" & datetime <= "2018-04-14")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4d <- as.numeric(mean_voltEXT_4d)
d_all$voltEXT <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , mean_voltEXT_4d, d_all$voltEXT)

@@

temp_to_replace <- d_all%>%
  dplyr::filter(datetime >= "2018-04-16 00:00:00" & datetime <= "2018-04-16 23:59:59")%>%
  dplyr::summarise( mean(temp_fb, na.rm = TRUE))
temp_to_replace <- as.numeric(temp_to_replace)
d_all$temp_fb <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , temp_to_replace, d_all$temp_fb)

# put also a temp insi value because FB was off FOR PERIOD ONE 2017-08-24
temp_to_replace <- d_all%>%
  dplyr::filter(datetime == "2017-08-24 12:00:00")%>%
  dplyr::summarise( mean(temp_insitu, na.rm = TRUE))
temp_to_replace <- as.numeric(temp_to_replace)
d_all$temp_insitu <- ifelse(d_all$datetime == "2017-08-24 13:00:00" , temp_to_replace, d_all$temp_insitu)

test <- d_all%>%
  dplyr::filter(datetime=="2017-08-24 13:00:00")
####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
                          calT = d_all$temp_insitu, calSal = d_all$sal_fb )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

# pH seaFET Final
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[20], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "follow")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

durPeriod <-  durPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 *24)))%>%
  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])

>>>>

sfPeriod <-  sfPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
  dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])

@@

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
                                ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
                                 ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
                                 ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[22], 21,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[23], 22,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[24], 23,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[25], 24,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[26], 25,
                                ifelse(datetime >= sfinterv[26] , 26,NA )))))))))))))))))))))))))))

@@

# # 5th period, with pH spectro at 2018-04-16 07:00:00 must fit one voltINT to calculate E0
# we put the mean of 4 following days because voltINT was not present.
mean_voltINT_4d <- d_all%>%
  dplyr::filter(datetime >= "2018-04-25" & datetime <= "2018-04-29")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4d <- as.numeric(mean_voltINT_4d)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2018-04-16 07:00:00" , mean_voltINT_4d, voltINT))

mean_voltEXT_4d <- d_all%>%
  dplyr::filter(datetime >= "2018-04-25" & datetime <= "2018-04-29")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4d <- as.numeric(mean_voltEXT_4d)
d_all$voltEXT <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , mean_voltEXT_4d, d_all$voltEXT)

@@

# put also a temp value because FB was off
temp_to_replace <- d_all%>%
  dplyr::filter(datetime >= "2018-04-16 00:00:00" & datetime <= "2018-04-16 23:59:59")%>%
  dplyr::summarise( mean(temp_fb, na.rm = TRUE))
temp_to_replace <- as.numeric(temp_to_replace)
d_all$temp_fb <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , temp_to_replace, d_all$temp_fb)

# put also a temp insi value because FB was off FOR PERIOD 1 : 2017-08-24
temp_to_replace <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 12:00:00" & datetime <= "2017-08-24 23:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
temp_to_replace <- as.numeric(temp_to_replace)
d_all$temp_insitu <- ifelse(d_all$datetime == "2017-08-24 14:00:00" , temp_to_replace, d_all$temp_insitu)

test <- d_all%>%
  dplyr::filter(datetime=="2017-08-24 14:00:00")

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
                          calT = d_all$temp_insitu, calSal = d_all$sal_fb )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

# pH seaFET Final
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
    dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= sfinterv[23], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[23], to= sfinterv[24], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[24], to= sfinterv[25], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[25], to= Sys.Date(), color = "#CCCCCC") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

#@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu)
# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
#     dySeries("phINT_filtered", label = "Raw pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
# 
#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dyLegend(show = "auto")   %>%
#   dyAxis( "y",valueRange = c(-1, 2))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL) 
#@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

@@

durPeriod <-  durPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 )))%>%
  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
